---
title: "UMAPs + Frequency plots + Violins"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
---


```{r}
source("src/00_library.R")
seu <- readRDS(paste0(dirs["rds"],"seu_corrected_clean.RDS"))
DefaultAssay(seu) <- "RNA"

# Define some variables to plot figures
variables <- c("seurat_clusters", "sample", "condition", "treatment")
features <- c("percent.mt", "nFeature_RNA", "nCount_RNA",
              "CD3E", "CD3D", "CD19", "NCAM1", "ITGAX", "CD14",
              "HLA-DRA", "HLA-DRB1","IL3RA")


# UMAPs
```{r}
for(variable in variables) {
  print(DimPlot(seu, reduction = "umap", group.by = variable, label = TRUE) +
    scale_color_manual(values=colors[[variable]][unique(seu@meta.data[[variable]])]))
}
```


# Frequency plots
```{r frequencies, echo=FALSE}
plot_freq_plot(seu$seurat_clusters, seu$condition,
               legend = "seurat_clusters", x_lab = "condition",
               palette = cluster_colors)
```


# Feature plots
```{r feature-plots, echo=FALSE, out.width=c("50%", "50%")}
for(feature in features) {
  if(isTRUE(feature %in% rownames(seu)) || isTRUE(feature %in% names(seu@meta.data))) {
    print(FeaturePlot(seu, reduction = "umap", features = c(feature)))
  } else {
    print(paste(feature, "not expressed in dataset."))
  }
}
```

